Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-11-28 hazelnut-popl17.tex
tweaks per publisher requests
fixed some bib entry formatting things
fixing spacing and missing citation

\def\OPTIONConf{1}%
\newif\iftr\trtrue
\RequirePackage{etex}
\documentclass[9pt]{sigplanconf}
\toappear{}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{ stmaryrd }
\usepackage{mathpartir}
\usepackage{balance}
\usepackage{stmaryrd}
\usepackage{wasysym}
\usepackage{multicol}
\usepackage{extarrows}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.9}
\usepackage{soul}
\setulcolor{red}
\usepackage{mathpazo}
\usepackage{colortab}
\usepackage[lowtilde]{url}
\usepackage{todonotes}
\usepackage{listings}
\lstset{tabsize=2,
basicstyle=\ttfamily\fontsize{8pt}{1em}\selectfont}
\usepackage{microtype}
\sloppy
\def \TirNameStyle #1{\small\rulename{#1}}
\renewcommand{\MathparLineskip}{\lineskiplimit=.3\baselineskip\lineskip=.3\baselineskip plus .2\baselineskip}

@@

\AtBeginDocument{%
 \abovedisplayskip=2pt
 \abovedisplayshortskip=0pt
 \belowdisplayskip=2pt
 \belowdisplayshortskip=0pt
}

@@

\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt}{4pt}{2pt}
\titlespacing*{\subsection}{0pt}{4pt}{2pt}
\titlespacing*{\subsubsection}{0pt}{4pt}{2pt}
\titlespacing*{\paragraph}{0pt}{4pt}{2pt}
\setlength{\skip\footins}{3pt plus 1px minus 5px}

@@

Interactive proof refinement systems, e.g. those in LCF \cite{Gordon:1978:MIP:512760.512773}, and more recent typed tactic systems, e.g. Mtac for Coq \cite{Ziliani:2013:MMT:2544174.2500579}, 
support an explicit model of a ``current'' typed hole that serves as the 
target of program synthesis. Hazelnut differs in that edits can occur anywhere within a term.

@@

\subsubsection{Programmable Actions}
Our language of actions is intentionally primitive. However, even now it
acts much like a simple imperative command language. This suggests future
expansion to, for example, a true \emph{action macro} language, whereby
functional programs could themselves be lifted to the level of actions to
compute non-trivial compound actions. Such compound actions would give a
uniform description of transformations ranging from the simple -- like
``move the cursor to the next hole to the right'' -- to quite complex whole
program refactoring, while remaining subject to the core Hazelnut
metatheory. Techniques like those in advanced tactic systems, e.g. Mtac, might be useful 
in proving these action macros correct \cite{Ziliani:2013:MMT:2544174.2500579}.

@@

\clearpage
\balance
\bibliographystyle{abbrvnat}
% The bibliography should be embedded for final submission.
\bibliography{bibliography}

>>>>

\def\OPTIONConf{1}%
\newif\iftr\trtrue
\RequirePackage{etex}
\documentclass[9pt]{sigplanconf}
\toappear{}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{ stmaryrd }
\usepackage{mathpartir}
\usepackage{balance}
\usepackage{stmaryrd}
\usepackage{wasysym}
\usepackage{multicol}
\usepackage{extarrows}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\definecolor{light-gray}{gray}{0.9}
\usepackage{soul}
\setulcolor{red}
\usepackage{mathpazo}
\usepackage{colortab}
\usepackage[lowtilde]{url}
\usepackage{todonotes}
\usepackage{listings}
\lstset{tabsize=2,
basicstyle=\ttfamily\fontsize{8pt}{1em}\selectfont}
\usepackage{microtype}
\sloppy
\def \TirNameStyle #1{\small\rulename{#1}}
\renewcommand{\MathparLineskip}{\lineskiplimit=.3\baselineskip\lineskip=.3\baselineskip plus .2\baselineskip}

@@

\AtBeginDocument{%
 \abovedisplayskip=2pt plus 4pt
 \abovedisplayshortskip=0pt
 \belowdisplayskip=2pt plus 4pt
 \belowdisplayshortskip=0pt
}

@@

\usepackage[compact]{titlesec}
\titlespacing*{\section}{0pt plus 3pt}{4pt plus 3pt}{2pt plus 3pt}
\titlespacing*{\subsection}{0pt plus 3pt}{4pt plus 3pt}{2pt plus 3pt}
\titlespacing*{\subsubsection}{0pt plus 3pt}{4pt plus 3pt}{2pt plus 3pt}
\titlespacing*{\paragraph}{0pt}{4pt}{3pt}
\setlength{\skip\footins}{3pt plus 1px minus 5px}

@@

Interactive proof refinement systems, e.g. those in LCF \cite{Gordon:1978:MIP:512760.512773}, and more recent typed tactic systems, e.g. Mtac for Coq \cite{ziliani2015mtac}, 
support an explicit model of a ``current'' typed hole that serves as the 
target of program synthesis. Hazelnut differs in that edits can occur anywhere within a term.

@@

\subsubsection{Programmable Actions}
Our language of actions is intentionally primitive. However, even now it
acts much like a simple imperative command language. This suggests future
expansion to, for example, a true \emph{action macro} language, whereby
functional programs could themselves be lifted to the level of actions to
compute non-trivial compound actions. Such compound actions would give a
uniform description of transformations ranging from the simple -- like
``move the cursor to the next hole to the right'' -- to quite complex whole
program refactoring, while remaining subject to the core Hazelnut
metatheory. Techniques like those in advanced tactic systems, e.g. Mtac, might be useful 
in proving these action macros correct \cite{ziliani2015mtac}.

@@

\balance
\bibliographystyle{abbrvnat}
% The bibliography should be embedded for final submission.
\bibliography{bibliography}

### 2016-11-28 implementation.tex
fixing spacing and missing citation

\subsection{HZ}
We have developed a simple reference implementation, HZ, of Hazelnut extended with sum types as described in Sec. \ref{sec:extending}.  In
order to reach a wide audience, we decided to implement HZ in the web
browser.  To take advantage of a mature implementation of the FRP
model, we chose to implement HZ using
OCaml\footnote{\url{https://ocaml.org/}}, the \texttt{js\_of\_ocaml}
compiler and associated libraries
\cite{DBLP:conf/ml/Balat06}\footnote{\url{http://ocsigen.org/js\_of\_ocaml/}}
and the OCaml React
library\footnote{\url{http://erratique.ch/software/react}}.

>>>>

\subsection{HZ}
We have developed a simple reference implementation, HZ, of Hazelnut extended with sum types as described in Sec. \ref{sec:extending}.  In
order to reach a wide audience, we decided to implement HZ in the web
browser.  To take advantage of a mature implementation of the FRP
model, we chose to implement HZ using
OCaml\footnote{\url{https://ocaml.org/}}, the OCaml React
library\footnote{\url{http://erratique.ch/software/react}}, and the \texttt{js\_of\_ocaml}
compiler and associated libraries
\cite{DBLP:conf/ml/Balat06}\footnote{\url{http://ocsigen.org/js\_of\_ocaml/}}.
